### 2024-03-04 Poster DPG/poster.tex
a
x

u

Paper stuff

data

stuff

tex

stuff

%MRW commands
\newcommand{\vect}[1]{\ensuremath{  \bm{#1}  } }
\newcommand{\Vint}[2]{\ensuremath{\mathcal{V}^{#1}_{\scriptscriptstyle #2}}}
\newcommand{\Veff}[2]{\ensuremath{\tilde{\mathcal{V}}^{#1}_{\scriptscriptstyle #2}}}

@@

\posterbox{2cm}{45cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
{%
\highlightOne{ Key ideas }
\begin{itemize}
\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
\item Write the Heisenberg EoM as matrix-vector EoM
\begin{equation*}
    \label{eqn:heisenberg}
    \begin{aligned}
        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= i \sum_j c_j(t) [H, \hat{A}_j] \\
        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
    \end{aligned}
\end{equation*}
\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
\begin{itemize}
    \item $\mM$ is nonnegative is thermal equilibrium
\end{itemize}
\end{itemize}

@@

\posterbox{2cm}{72.5cm}{38cm}{Model}
{%
\begin{minipage}{0.59\textwidth}
    \highlightOne{ Hamiltonian: Extended Hubbard model }
    \begin{equation*}
        \label{eqn:full_hamiltonian}
        \begin{aligned}
            H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
            + \mu \sum_{i,\sigma} n_{i\sigma} \\
            &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
            + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
        \end{aligned}
    \end{equation*}
    \begin{itemize}
        \item Half-filling, on both a square and a simple cubic lattice, temperature $T=0$
    \end{itemize}
    \highlightOne{ Static mean-field theory }
    \begin{itemize}
        \item Used to deal with the interaction terms and to obtain expectation values for iEoM
        \item Terms depend on $\hat{\gamma}(\vec{k}) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)$ \\
        $\Rightarrow$ DOS based description $\rho \coloneqq \frac{1}{N} \sum_{\vec{k}} \delta(\gamma - \hat{\gamma}(\vec{k}))$
        \begin{align*}
            \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\sigma} \int \langle g_{\sigma} (\gamma) \rangle \dgamma\\\ 
            \Delta_\text{SC} &= \frac{U}{N} \int \langle f(\gamma) \rangle \dgamma\\
            \Delta_\text{AFM} &= \frac{U}{2N} \int \left( \langle g_{\uparrow} (\gamma) \rangle - \langle g_{\downarrow} (\gamma) \rangle \right) \dgamma\\ 
            \Delta_n &= \frac{V}{N} \sum_{\sigma} \int \gamma \langle n_{\sigma} (\gamma) \rangle \dgamma
        \end{align*}
        \item Allows us to tackle both 2D and 3D systems
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{plots/phase_diagram.pdf}
    \center{\textcolor{tudarkgreen}{Mean-field phase diagram of the extended Hubbard model. 
    (a) Square lattice (b) simple cubic lattice. $d_{x^2-y^2}$ from Ref. \cite{Micnas88b}.}}
\end{minipage}
\highlightOne{ Phase diagram }
\begin{itemize}
    \item Mostly the same for both lattices, $d_{x^2 -y^2}$-wave SC for $V<0$ on the square lattice is inaccessible to us
    \item Red region: Mean-field self-consistency converges to $s$-wave SC, but $\mM$ is not nonnegative $\Rightarrow$ not the true groundstate.
    Literature suggests a phase-separated state. \cite{Linner23}
    \item Purple region: Inaccuracies due to finite discretization dominate; here the gap is of the same order of magnitude as our gap
\end{itemize}
}

@@

\posterbox{42cm}{78cm}{38cm}{Behavior of the peaks}
{%
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/sc_peak_in_cdw.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the SC spectral functions in the CDW phase.}}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/cdw_peak_in_sc.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the CDW spectral functions in the SC phase.}}
\end{minipage}
\begin{itemize}
    \item Double-logarithmic plots
    \item The weights diverge as $1/\sqrt{|V|}$ while the peak positions move to $0$ as $\sqrt{|V|}$
    \item For $V\gg t$, the weights become constant. The position grows linearly and the position in units of the gap becomes constant.
\end{itemize}

\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the AFM and CDW spectral functions close to the phase transition.}}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
    \begin{itemize}
        \item Orange region: System is in the CDW phase, blue region: System is in the AFM phase
        \item Peak position grows linearly with $U$ as the system moves away from the phase transition
        \item But it moves into the continuum (b) quadratically
        \item At the same time, the weights also vanish
    \end{itemize}
\end{minipage}

@@

\posterbox{2cm}{106cm}{38cm}{Possible outlook}
{%
\begin{itemize}
\item Incorporating phase-separated states into the mean-field theory, thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
\item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
\item Describing multi-band systems with even richer phases and collective excitations
\end{itemize}
}

\posterbox{42cm}{110cm}{38cm}{References}
{%
\begingroup
\renewcommand{\section}[2]{}	% for removing the bibliography title
\begin{thebibliography}{99}
    %\begin{multicols}{2}
    \bibitem{Kalthoff17} M. Kalthoff, F. Keim, H. Krull, and G. S. Uhrig, The European Physical Journal B 90, 97 (2017).
    \bibitem{Bleicker18} P. Bleicker and G. S. Uhrig, Phys. Rev. A 98, 033602 (2018).
    \bibitem{Micnas88b} R. Micnas, J. Ranninger, S. Robaszkiewicz, and S. Tabor, Phys. Rev. B 37, 9410 (1988).
    \bibitem{Linner23} E. Linnér, C. Dutreix, S. Biermann, and E. A. Stepanov, Phys. Rev. B 108, 205156 (2023).
    %\end{multicols}          
\end{thebibliography}
\endgroup
}

>>>>

@@

\posterbox{2cm}{46cm}{38cm}{Method: Iterated equations of motion (iEoM) \cite{Kalthoff17,Bleicker18}}
{%
\highlightOne{ Key ideas }
\begin{itemize}
\item Consider a time-dependent operator $\hat{a}(t) = \sum_j c_j(t) \hat{A}_j$ and the symplectic product $(\hat{A} | \hat{B}) \coloneqq \langle [\hat{A}^\dagger, \hat{B}] \rangle$
\item Write the Heisenberg EoM as matrix-vector EoM
\begin{equation*}
    \label{eqn:heisenberg}
    \begin{aligned}
        \ddt \hat{a}(t) = \sum_j \ddt c_j(t) \hat{A}_j &= i \sum_j c_j(t) [H, \hat{A}_j] \\
        \Rightarrow \sum_j \underbrace{(\hat{A}_i | \hat{A}_j)}_{\coloneqq \mN_{ij}} \ddt c_j(t) &= i \sum_j \underbrace{(\hat{A}_i | [\hat{H}, \hat{A}_j])}_{\coloneqq \mM_{ij}} c_j(t) \\
        \Rightarrow \mN \ddt \vec{c}(t) &= i \mM \vec{c}(t)\,.
    \end{aligned}
\end{equation*}
\item Generalized eigenvalue problem $\omega \mN \vec{v} = \mM \vec{v}$, real solutions if either $\mM$ or $\mN$ is nonnegative.
\begin{itemize}
    \item $\mM$ is nonnegative is thermal equilibrium
\end{itemize}
\end{itemize}

@@

\posterbox{2cm}{74.8cm}{38cm}{Model}
{%
\begin{minipage}{0.59\textwidth}
    \highlightOne{ Hamiltonian: Extended Hubbard model }
    \begin{equation*}
        \label{eqn:full_hamiltonian}
        \begin{aligned}
            H = &-t \sum_{\langle i, j \rangle, \sigma} \left( c_{i\sigma}^\dagger c_{j\sigma} + \text{h.c.} \right) 
            + \mu \sum_{i,\sigma} n_{i\sigma} \\
            &+ U \sum_{i} n_{i\uparrow} n_{i\downarrow} 
            + \frac{V}{2} \sum_{\langle i, j\rangle, \sigma} n_{i\sigma} n_{j\sigma}\,,
        \end{aligned}
    \end{equation*}
    \begin{itemize}
        \item Half-filling, on both a square and a simple cubic lattice, temperature $T=0$
    \end{itemize}
    \highlightOne{ Static mean-field theory }
    \begin{itemize}
        \item Used to deal with the interaction terms and to obtain expectation values for iEoM
        \item Terms depend on $\hat{\gamma}(\vec{k}) \coloneqq \frac{1}{D} \sum_{\alpha=1}^D \cos(k_\alpha)$ \\
        $\Rightarrow$ DOS based description $\rho \coloneqq \frac{1}{N} \sum_{\vec{k}} \delta(\gamma - \hat{\gamma}(\vec{k}))$
        \begin{align*}
            \Delta_\text{CDW} &= \left(\frac{U}{2N} - \frac{zV}{N}\right) \sum_{\sigma} \int \langle g_{\sigma} (\gamma) \rangle \dgamma\\\ 
            \Delta_\text{SC} &= \frac{U}{N} \int \langle f(\gamma) \rangle \dgamma\\
            \Delta_\text{AFM} &= \frac{U}{2N} \int \left( \langle g_{\uparrow} (\gamma) \rangle - \langle g_{\downarrow} (\gamma) \rangle \right) \dgamma\\ 
            \Delta_n &= \frac{V}{N} \sum_{\sigma} \int \gamma \langle n_{\sigma} (\gamma) \rangle \dgamma
        \end{align*}
        \item The iEoM utilize the same description
        \item Allows us to tackle both 2D and 3D systems
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}{0.4\textwidth}
    \includegraphics[width=\textwidth]{plots/phase_diagram.pdf}
    \center{\textcolor{tudarkgreen}{Mean-field phase diagram of the extended Hubbard model. 
    (a) Square lattice (b) simple cubic lattice. $d_{x^2-y^2}$ from Ref. \cite{Micnas88b}.}}
\end{minipage}

\highlightOne{ Phase diagram }
\begin{itemize}
    \item Mostly the same for both lattices, $d_{x^2 -y^2}$-wave SC for $V<0$ on the square lattice is inaccessible to us
    \item Red region: Mean-field self-consistency converges to $s$-wave SC, but $\mM$ is not nonnegative $\Rightarrow$ not the true groundstate.
    Literature suggests a phase-separated state. \cite{Linner23}
    \item Purple region: Inaccuracies due to finite discretization dominate; here the gap is of the same order of magnitude as our gap
\end{itemize}
}

@@

\posterbox{42cm}{78cm}{38cm}{Behavior of the peaks}
{%
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/sc_peak_in_cdw.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the SC spectral functions in the CDW phase.}}
\end{minipage}
\hfill
\begin{minipage}{0.49\textwidth}
    \includegraphics[width=\textwidth]{plots/cdw_peak_in_sc.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the CDW spectral functions in the SC phase.}}
\end{minipage}
\begin{itemize}
    \item Double-logarithmic plots $\Rightarrow y(V) = e^d |V|^c$
    \item The weights diverge as $1/\sqrt{|V|}$ while the peak positions move to $0$ as $\sqrt{|V|}$
    \item For $V\gg t$, the weights become constant. The position grows linearly and the position in units of the gap becomes constant.
\end{itemize}

\begin{minipage}{0.55\textwidth}
    \includegraphics[width=\textwidth]{plots/afm_cdw_peaks_overview.pdf} % NV sketch
    \center{\textcolor{tudarkgreen}{Weight and position of the peak in the AFM and CDW spectral functions close to the phase transition.}}
\end{minipage}
\hfill
\begin{minipage}{0.44\textwidth}
    \begin{itemize}
        \item Orange region: System is in the CDW phase, blue region: System is in the AFM phase
        \item Peak position grows linearly with $U$ as the system moves away from the phase transition
        \item But it moves into the continuum (b) quadratically
        \item At the same time, the weights also vanish
    \end{itemize}
\end{minipage}

@@

\posterbox{2cm}{110.35cm}{38cm}{Possible outlook}
{%
\begin{itemize}
\item Incorporating phase-separated states into the mean-field theory
\begin{itemize}
    \item thereby providing deeper analysis of the negative $V$ regime of phase diagrams and collective excitations
\end{itemize}
\item Coupling the electronic system to the electromagnetic field to include the Anderson-Higgs mechanism for superconductors
\item Describing multi-band systems with even richer phases and collective excitations
\end{itemize}
}

\posterbox{42cm}{111cm}{38cm}{References}
{%
\begingroup
\renewcommand{\section}[2]{}	% for removing the bibliography title
\begin{thebibliography}{99}
    %\begin{multicols}{2}
    \bibitem{Kalthoff17} M. Kalthoff, F. Keim, H. Krull, and G. S. Uhrig, The European Physical Journal B 90, 97 (2017).
    \bibitem{Bleicker18} P. Bleicker and G. S. Uhrig, Phys. Rev. A 98, 033602 (2018).
    \bibitem{Micnas88b} R. Micnas, J. Ranninger, S. Robaszkiewicz, and S. Tabor, Phys. Rev. B 37, 9410 (1988).
    \bibitem{Linner23} E. Linnér, C. Dutreix, S. Biermann, and E. A. Stepanov, Phys. Rev. B 108, 205156 (2023).
    %\end{multicols}          
\end{thebibliography}
\endgroup
}
